\chapter{List of abbreviations and symbols}

\begin{description}
    \item[AI] (Artificial Intelligence) is a type of computer software which is capable of learning how to resolve problems.
    \item[Search algorithm] is a type of algorithm which is used for searching process in data structures. Examples of search algorithms are: min-max, max, min etc.
    \item[Game tree leaf] is a node in the last layer of the structure.
    \item[Feature map] is a matrix that is an output of convolutional layer. 
    \item[IDE] (Integrated Development Environment) is a software application that provides comprehensive facilities to computer programmers for software development.
    \item[PGN] (Portable Game Notation) is a standard text based notation to records chess games (those files includes not only moves but additional data related to this game).
    \item[ELO] is an rating system which allows for calculating the relative skill levels of players in games such as chess. This rating system is also often use in video games.
    \item[Epoch] is a name of the single model training iteration. This training iteration consists of \textbf{train} (process all training data and update weights values) and \textbf{test} (process test set and calculate accuracy of the model).
\end{description}
% \begin{itemize}
% \item[DNA] deoxyribonucleic acid
% \item[MVC] model--view--controller 
% \item[$N$] cardinality of data set
% \item[$\mu$] membership function of a fuzzy set
% \item[$\mathbb{E}$] set of edges of a graph
% \item[$\mathcal{L}$] Laplace transformation
% \end{itemize}